Neural Power Unit \\-- A Bayesian Approach To Neural Arithmetic

### 2020-05-15 papers/main.tex
paper update

@@

\begin{abstract}
  Common Neural Networks poorly approximate simple arithmetic operations.  The
  new Neural Arithmetic Units aim to overcome this difficulty, but are limited
  either limited to operate on positive numbers (NALU by
  \citet{trask_neural_2018}), or can only represent simple addition and
  multiplication (NAU \& NMU by \citet{madsen_neural_2020}).
  We present the first Neural Arithmetic Unit that operates on the full domain
  of real numbers and is capable of learning arbitrary power functions.
  For a theoretically grounded sparsification of the units we employ Bayesian
  compression on the model weights via Automatic Relevance Determination.
\end{abstract}

@@

It is known that Neural Networks can approximate functions arbitrarily
well\todo{cite universal approx}.  However, this strength of approximation
often comes at the cost of generalization beyond the training data manifold.
This lack of generalization of traditional network architectures becomes 
The inability to generalize to unseen inputs is an indicator for a lack of
abstraction of the task at hand. The model merely sort of memorized the inputs.
Neural Arithmetic Units aim to

\todo{mention ODEs as use case}

@@

\citet{trask_neural_2018} have demonstrated how severe the extrapolation problem is even for
the simplest arithmetic operations, such as summing or multiplying two numbers.
In order to increase the power of abstraction of Neural Networks they propose a
\emph{Neural Arithmetic Logic Unit} (NALU) which can help to overcome this
problem \cite{trask_neural_2018} and is capable of learning the arithmetic
addition, subtraction, multiplication, and division
$\{+,-,\times,\div\}$ with stunning extrapolation accuracy.  However,
the NALU comes with the severe limitation not being able to handle negative
inputs due to the logarithm in the multiplication part of the NALU:

@@

@@

\subsection{Gradient surfaces}%
\label{sub:gradient_surfaces}
\begin{figure}
  \centering
  %\includegraphics[width=0.8\linewidth]{../plots/test.pgf}
  \input{../plots/test.tikz.tex}
  \caption{Test}%
  \label{fig:test}
\end{figure}

>>>>

\usepackage{booktabs}
\renewcommand{\arraystretch}{1.2}

@@

\begin{abstract}
  Common Neural Networks can approximate simple arithmetic operations, but fail
  to generalize well beyond the training manifold. A new class of units called
  \emph{Neural Arithmetic Units} aim to overcome this difficulty, but are limited
  either to operate on positive numbers (NALU by
  \citet{trask_neural_2018}), or can only represent simple addition and
  multiplication (NAU \& NMU by \citet{madsen_neural_2020}).
  We present the first Neural Arithmetic Unit that operates on the full domain
  of real numbers and is capable of learning arbitrary power functions.
\end{abstract}

@@

Neural Networks (NN) have proven to perform exceptionally well at function
approximation tasks\todo{cite universal approx}. The great approximation
performance unfortunately come at the cost of generalization beyond the
training domain\todo{cite something?}.  The inability to generalize to unseen
inputs is a fundamental problem that hints at a lack of \emph{understanding} of
the given task. The model merely memorizes the seen inputs and fails to
abstract the true learning task.

Neural Arithmetic Units aim to overcome this problem with units that are able
to represent simple arithmetic operations exactly. By composition of these
units it becomes possible to learn e.g. exponentials, sinus functions,
logarithms, etc. This promises to improve on the extrapolation capabilities of
NNs even on tasks that are beyond artificial arithmetic tasks such as learning
multiplication, or a certain power function \todo{cite some examples}.
\todo{mention ODEs as use case}

@@

\citet{trask_neural_2018} have demonstrated how severe the extrapolation
problem is even for the simplest arithmetic operations, such as summing or
multiplying two numbers.  In order to increase the power of abstraction of NNs
they propose a \emph{Neural Arithmetic Logic Unit} (NALU) which is capable of
learning arithmetic addition, subtraction, multiplication, and division
$\{+,-,\times,\div\}$ with stunning extrapolation accuracy.  However, the NALU
comes with the severe limitation not being able to handle negative inputs due
to the logarithm in the multiplication part of the NALU:

@@

\begin{table}
  \centering
  \caption{Comparison of different $2\times2$ layers on the task $(x,y)\rightarrow(xy,\frac{x}{y})$.
  $(x,y) \in \mathcal U^2(-2,2)$}
  \label{tab:label}
  \input{table_x*y_xdivy.tex}
\end{table}

@@

\subsection{Gradient surfaces}%
\label{sub:gradient_surfaces}
% \begin{figure}
%   \centering
%   %\includegraphics[width=0.8\linewidth]{../plots/test.pgf}
%   \input{../plots/test.tikz.tex}
%   \caption{Test}%
%   \label{fig:test}
% \end{figure}
